Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-02-25 ECCV/paper.tex
Expanded Related Work

\begin{abstract}
Fiducial markers are commonly used to track an object in an unknown environment
and finds use in various applications in Virtual Reality, Medical imaging,
Surveys, etc. The performance of popular fiducials is satisfactory when there is
little motion or no motion in the device obtaining the imagery. But when there
is continuous and swift motion, as in the case of low cost quadcopters,
performance of these fiducials degrade significantly due to motion blur.
Inspired from Circular Data Matrix\cite{NaimarkF02} we have designed a fiducial
that may be thought of as a binary code.  It contains concentric white rings of
equal widths on a black background with a blurred border. Our
algorithm is based on the fact that there is no blur in the direction
perpendicular to the direction of the motion.
\dots
\keywords{Fiducials, Blur Invariant Tracking,}
\end{abstract}

@@

Low cost quadcopters such as AR Drone are very unstable which causes non-uniform
motion resulting lot of motion blur in captured images. Also, as image transfer
is done through wireless media using UDP, there is possibility of missing 
intermediate frames . It results in lower frame rate (maximum 20-25 frames per
second (FPS)) instead of normal rate of 30 FPS. This dropping of frames may
cause drastic change in position of object in successive frames. Thus,
performance of traditional tracking methods is not satisfactory for tracking
through quadcopters. Our aim is to design a fiducial which we will be able to
track under significant amount of motion blur and is robust in terms of drastic
change in its position in successive frames.

@@

\section{Related Work}
The ARToolkit \cite{ARToolkit02} \cite{kato-artoolkit} is well known toolkit in
AR system, widely used to find pose of the object on which it is placed.
Fiala et.al \cite{Fiala05} developed fiducial named, ARTag, bi-tonal system
containing 2002 planar markers, each consisting of a square border and an
interior region filled with a 6x6 grid of black or white cells. It proved to be
more efficient than \cite{ARToolkit02} in terms of detection rate as well as the
number of different patterns which can be created.

Concentric Rings\cite{NaimarkF02} \\
Multicolor rings \cite{Cho:2001} \cite{Cho97fastcolor} \\
Circular Data Matrix Fiducial System \cite{NaimarkF02} \\

Zhang el. al.\cite{Zhang:2002} and Claus et. al. \cite{ClausF04} have done
quite comprehensive comparative study of various fiducial marker systems with
respect to processing time, recognition rate and accuracy with
respect to viewing angle and distance.

RUNE-Tag \cite{runetag11} \\
Pi-Tag \cite{Pitag13} \\
Blut \cite{Wu:2011}

@@

\begin{figure}
\centering
  \includegraphics[width=.2\linewidth]{newconcentric_00.pdf}  
  \includegraphics[width=.2\linewidth]{newconcentric_01.pdf}
  \includegraphics[width=.2\linewidth]{newconcentric_10.pdf}
  \includegraphics[width=.2\linewidth]{newconcentric_11.pdf}
  \caption{Two bit binary coded Fiducials (from left to right: Binary Code 00,
  Binary Code 01, Binary Code 10, Binary Code 11)}
  \label{fig:fiducials}
\end{figure}

\section{Fiducial Detection Algorithm}
Overall flow of fiducial detection algorithm can be summarised as follows:
\begin{itemize}
  \item Apply Gabor Filter on input image
  \item Find Connected components in Gabor output
  \item Cluster the connected components in bounding box
  \item Detect code in the bounding box
  \begin{itemize}
    \item Run PCA on Gabor output in bounding box
    \item Find intensity profile along first principal component passing through
    centroid
    \item If there are less than four black to white transitions in the
    intensity profile, ignore the bouding box
    \item Otherwise, classify the detected code by the classifer trained on
    standards.
  \end{itemize}
\end{itemize}

\textbf{Gabor Filter}: A 2D Gabor filter is a Gaussian kernel function modulated
by a sinusoidal plane wave. It is used to find high gradient patches from the
image. In our case, it will detect blur invariant sections of the fiducials. We
have applied Gabor filter for eight different orientations and then calculated
L2 norm of all outputs.

@@

\textbf{PCA}: Principal Component Analysis is done on the clustered Gabor
output. Along 1st principal component, intensity profile in the original image is found.
Number of transitions in the intensity profile will give us the number of rings.

@@

\section{Discussion}

\section{Conclusion and Future Work}

Pose Estimation

>>>>

\begin{abstract}
Fiducial markers are commonly used to track an object in an unknown environment
and finds use in various applications in Virtual Reality, Medical imaging,
Surveys, etc. The performance of popular fiducials is satisfactory when there is
little motion or no motion in the device obtaining the imagery. But when there
is continuous and swift motion, as in the case of low cost quadcopters,
performance of these fiducials degrade significantly due to motion blur.
Inspired from Circular Data Matrix\cite{NaimarkF02}, we have designed a fiducial
that may be thought of as a binary code. It contains concentric white rings of
equal widths on a black background with a blurred border. Our fiducial detection
algorithm is based on the fact that there is no blur in the direction
perpendicular to the direction of the motion. We will show through experimental
validation that our fiducial works better than popular fiducials such as
ARTag under signifacant motion blur.

\keywords{Fiducials, Tracking, Blur Invariant}
\end{abstract}

@@

Low cost quadcopters such as AR Drone are very unstable which causes non-uniform
motion resulting lot of motion blur in captured images. Also, as image transfer
is done through wireless media using User Datagram Protocol (UDP), there is
possibility of missing intermediate frames . It results in lower frame rate
(around 15 frames per second (FPS)) instead of normal rate of 30 FPS. This
frequent dropping of frames may cause drastic change in position of object in
successive frames. Thus, performance of traditional tracking methods is not
satisfactory for tracking through quadcopters. Our aim is to design a fiducial
which we will be able to track under significant amount of motion blur and is
robust in terms of drastic change in its position in successive frames.

@@

\section{Related Work}
The ARToolkit \cite{ARToolkit02} \cite{kato-artoolkit} is well known toolkit in
Augmented Reality system, widely used to find pose of the object on which it is
placed.  Fiala et al. \cite{Fiala05} developed fiducial named, ARTag, bi-tonal
system containing 2002 planar markers, each consisting of a square border and
an interior region filled with a 6x6 grid of black or white cells. It proved to
be more efficient than \cite{ARToolkit02} in terms of marker recognition rate
as well as the number of different patterns which can be created.

Concentric Rings are reported used first by Gatrell et al.\cite{concentric} for
monocular pose estimation as well as object identification in space. Cho et al.
\cite{Cho:2001}\cite{Cho97fastcolor} have used multi color rings in wide area
tracking in large scale applications. In \cite{NaimarkF02}, Naimark et al.
have developed ``Circular Data Matrix Fiducial System'', for wide area tracking.

Zhang el. al.\cite{Zhang:2002} and Claus et al. \cite{ClausF04} have done
quite comprehensive comparative study of various fiducial marker systems with
respect to processing time, recognition rate and accuracy with
respect to viewing angle and distance.

Bergamasco et al. \cite{runetag11} developed RUNE-Tag, fiducial marker
system which works under large amount of occlusion. Bergamasco et al. also 
designed Pi-Tag \cite{Pitag13}, marker design based on projective
invariants.
Wu et al.\cite{Wu:2011} have developed BLUr-driven Tracker (BLUT) framework for
tracking motion-blurred targets.

@@

\begin{figure}
\centering
  \includegraphics[width=.22\linewidth]{newconcentric_00.pdf}  
  \includegraphics[width=.22\linewidth]{newconcentric_01.pdf}
  \includegraphics[width=.22\linewidth]{newconcentric_10.pdf}
  \includegraphics[width=.22\linewidth]{newconcentric_11.pdf}
  \caption{Two bit binary coded Fiducials (from left to right: Binary Code 00,
  Binary Code 01, Binary Code 10, Binary Code 11)}
  \label{fig:fiducials}
\end{figure}

\section{Fiducial Detection Algorithm}
Our fiducial detection strategy is different from \cite{NaimarkF02} and works
under significant amount of blur. Our algorithm is based on the fact that there
is no blur in the direction perpendicular to the direction of the motion.
Overall flow of fiducial detection algorithm can be summarised as follows:
\begin{itemize}
  \item Apply Gabor Filter on input image
  \item Find Connected components in Gabor output
  \item Cluster the connected components in bounding box
  \item Detect code in the bounding box
  \begin{itemize}
    \item Run PCA on Gabor output in bounding box
    \item Find intensity profile along first principal component passing through
    centroid
    \item If there are less than four black to white transitions in the
    intensity profile, ignore the bouding box
    \item Otherwise, classify the detected code by the classifer trained on
    standards.
  \end{itemize}
\end{itemize}

\textbf{Gabor Filter}: A 2D Gabor filter is a Gaussian kernel function modulated
by a sinusoidal plane wave. It is used to find high gradient patches from the
image. In our case, it will detect blur invariant sections of the fiducials. We
have applied Gabor filter for eight different orientations ($\theta = 0, 45,
90, 135, 180, 225, 270, 315$) and then calculated L2 norm of all outputs.

@@

\textbf{PCA}: Principal Component Analysis is done on the clustered Gabor
output. Along first principal component, intensity profile in the original image
is found. Number of transitions in the intensity profile will give us the
number of rings.

@@

\section{Discussion}
\begin{itemize}
\item Processing Time
\item False Positives and False Negatives
\item Pose Estimation
\end{itemize}
\section{Conclusion and Future Work}
